---
title: "Shopping list for people with dietry restrictions"
author: "Aleksandra Mazij, Kamil Maćków"
date: "`r format(Sys.time(), '%m/%d/%Y %X')`"
output:
  rmdformats::readthedown:
    highlight: kate
    number_sections: true
    self_contained: true
---

```{r setup, include=FALSE}
## Global options
library(knitr)
library(rmdformats)
library(formatR)
opts_chunk$set(echo = TRUE, 
               cache = FALSE,
               prompt = FALSE,
               tidy = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE,
               fig.width = 7.4,
               fig.height = 4.7,
               fig.align = "center")
opts_knit$set(width = 80)
```

```{r, code = readLines("../data_preparation.R"), include=FALSE}
```

To use this template, install the package: `install.packages("rmdformats")`


# Introduction

In response to the increasing need for personalized nutrition, our project focuses on developing a practical solution for individuals with dietary restrictions. Using web scraping techniques, we gather a diverse range of recipes from `https://kuchnialidla.pl/przepisy/dania-glowne` and filter out those containing restricted products.

To get the restricted products we also scraped a website containing dietary information: `https://www.tabelakalorii.net/zywnosc`. As the lists were not matching fully with all the ingredients used in our recipes, we had to add some keywords manually to the set of restricted products.

The outcome of our scraper is a data frame of "allowed" recipes, ensuring compliance with specific dietary needs. Our script then identifies common ingredients across these recipes to create a streamlined and personalized shopping list. This approach not only caters to individual dietary preferences but also enhances the efficiency of meal planning, offering a user-friendly solution at the intersection of technology and nutrition.


# Web scraping methodology

The web scraping part of our project was executed through the dedicated script **scraper.R**. In its initial phase, the script gathered URLs for the recipes sub-domains. Focusing exclusively on main dishes for the current project scope, we navigated through these links to compile an exhaustive data set. Following the acquisition of main dish link addresses, we proceeded to extract essential details such as ingredients and macro information (which wasn't used in this project but may be useful in case of a future further development).

Subsequently, our script extended its capabilities to scrape information on restricted products from another website. Additionally, we manually incorporated some products. It's noteworthy that the manually added lists did not align perfectly with all the ingredients utilized in our recipes.

Throughout this process, GET() served as the main function for retrieving information, ensuring efficiency and accuracy in data extraction. The dual approach of automated scraping and manual supplementation contributes to the robustness of our data set, providing a solid foundation for analysis and potential expansion.

- First 3 dishes of our scraped **recipes** data frame:
```{r}
head(recipes$Name, 3)
```

- Respective 3 ingredients lists:
```{r}
head(recipes$Ingredients, 3)
```

- Some 3 restricted ingredients for a dairy free person
```{r}
head(dairy_excluded_products, 3)
```


# Extracting only valid recipes 

Taking restricted products into account for a specific diet, we successfully excluded recipes containing those items using the **stringdist** function. Upon reviewing the remaining valid recipes, it is evident that the exclusion process was effective, yielding the desired outcomes. The next step involves identifying the most frequently occurring ingredients among these validated recipes. Here are some of the recipes valid for a person who doesn't consume dairy:

```{r}
head(valid_recipes_for_dairy_free$Name, 5)
```


# Finding most often used ingredients in the valid recipes

In order to create a shopping list for a person with certain dietary restrictions...

```{r}
head(best_products_dairy_free, 15)
```


# Searching for recipes with these products

....
```{r}
head(possible_recipes_from_products_dairy_free, 15)
```

# Some charts (?)

# Conclusions
