---
title: "Shopping list for people with dietry restrictions"
author: "Aleksandra Mazij, Kamil Maćków"
date: "`r format(Sys.time(), '%m/%d/%Y %X')`"
output:
  rmdformats::readthedown:
    highlight: kate
    number_sections: true
    self_contained: true
---

```{r setup, include=FALSE}
## Global options
library(knitr)
library(rmdformats)
library(formatR)
opts_chunk$set(echo = TRUE, 
               cache = FALSE,
               prompt = FALSE,
               tidy = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE,
               fig.width = 7.4,
               fig.height = 4.7,
               fig.align = "center")
opts_knit$set(width = 80)
```

To use this template, install the package: `install.packages("rmdformats")`

# Chapter ONE

To assess the project, please submit the following files - of course, compress them beforehand (you can use, for example, the free 7-zip):

-   `scraper.R` file and other files that were used to scrape data (e.g., `function.R`) or to clean them (`munging.R`).
-   The data obtained through web scraping (uncleaned) as well as the data that have been prepared for writing the report. These data should be saved in `CSV` files.
-   `Surname.Rmd` file, which was the basis for preparing the report.
-   An `HTML` file that was created by compiling the Rmd file.
-   Note: everything must be done in R.

Remember to load the necessary packages at the very beginning. Write R codes in so-called chunks. To add them, you can use the shortcut: CTRL+ALT+I

```{r}
# library(tidyverse)
# elon <- read_csv("dane/twitterElonMusk.csv")
# head(elon)
```

Let's creat a chart.

```{r}
# kable(mtcars[1:5, ])
# ggplot(mtcars, aes(x = mpg, y = qsec)) + theme_bw() +
#    geom_point(size = 4)
```

## Subchapter

Mark up text:

-   italic type: *this is the first*, and this is the *second award*.
-   bold type: **this is the first**, and this is the **second award**.

### Some bullet points

List

-   item 1
-   item 2
-   item 3

Or maybe this?

1.  point 1
2.  point 2
3.  point 3

## Another

# Chapter TWO

Or perhaps you would like to highlight the highest value from the `hp` column in the description? The maximum, i.e., `x` horsepower, is observed in a car in row `y`.
